---
title: "Assignment 2"
---

### Question 1
```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Loading necessary libraries

library(tidyverse)
library(stringr)
library(rvest)
library(ggplot2)
library(knitr)
library(reshape2)
library(dplyr)
library(magrittr)
library(kableExtra)



# Defining the url before 2010
login_url_1 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"

# Defining the url years between 2010 and now
login_url_2 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-28&num_votes=2500,&country_of_origin=TR&count=250"

```

### Question 2
```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Fonksiyon: IMDb verilerini çekme ve temizleme
scrape_imdb_data <- function(url) {
  data <- read_html(url)
  
  name <- data %>%
    html_nodes('.ipc-title__text') %>%
    html_text()
  
  rating <- data %>%
    html_nodes('.ipc-rating-star--base') %>%
    html_attr('aria-label') %>%
    str_extract("\\d+\\.\\d+|\\d+") %>%
    map_dbl(~ ifelse(is.na(.x), NA_real_, as.numeric(.x)))
  
  year <- data %>%
    html_nodes(xpath = '//*[contains(@class,"sc-43986a27-7")]') %>%
    html_text() %>%
    str_extract("\\d{4}") %>%
    map_dbl(~ ifelse(is.na(.x), NA_real_, as.numeric(.x)))
  
  duration <- data %>%
    html_nodes(xpath = '//*[contains(@class,"sc-43986a27-7")]') %>%
    html_text() %>%
    str_extract("\\d+h \\d+m|\\d+h") %>%
    str_replace_all("h", ":") %>%
    str_replace_all("m", "") %>%
    str_replace_all("^(:\\d+)$", "0\\1") %>%  # Sadece dakika varsa, saat olarak "0" ekleyin
    str_split(":") %>%
    map_dbl(~ sum(as.numeric(.x) * c(60, 1), na.rm = TRUE))

  
  vote <- data %>%
    html_nodes('.kRnqtn') %>%
    html_text() %>%
    parse_number()
  
  # Uzunluğu eşitlemek için kırpma işlemi
  min_length <- min(length(name), length(rating), length(year), length(duration), length(vote))
  name <- name[1:min_length]
  rating <- rating[1:min_length]
  year <- year[1:min_length]
  duration <- duration[1:min_length]
  vote <- vote[1:min_length]
  
  return(data.frame(name, rating, year, duration, vote))
}

# Verileri çekme
movies_1 <- scrape_imdb_data(login_url_1)
movies_2 <- scrape_imdb_data(login_url_2)
movies <- bind_rows(movies_1, movies_2)

# Sonuçları kontrol etme
print(head(movies, 10))
```

### Question 3

# a-)

```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Sorting movies by rating
sorted_movies <- movies %>% arrange(desc(rating))

# Top 5 movies
top_5_movies <- head(sorted_movies, 5)

# Bottom 5 movies
bottom_5_movies <- tail(sorted_movies, 5)

# Displaying the results
top_5_movies
bottom_5_movies


```
I've watched two of them, and I believe the ratings are accurate.

I haven’t watched any of them

# b-)

Here are my top three favorite movies from that list.
```{r}
#| code-fold: true
#| code-summary: "Show the code"
# List column names in your data frame

my_movies <- movies_df[movies_df$movie_titles %in% c("Ayla: The Daughter of War", "Babam ve Oglum", "Mucize"), ]
my_movies


```
# c-)

```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Veri setinizdeki eksik değerleri dikkate alarak, yıllık ortalama puanları ve film sayısını hesaplayın
yearly_averages <- movies %>%
  drop_na(rating) %>%  # Eksik puanları içermeyen satırları seçin
  group_by(year) %>%
  summarise(average_rating = mean(rating),
            movie_count = n())

# Yıllık ortalama puanların dağılımını gösteren bir saçılma grafiği oluşturun
ggplot(yearly_averages, aes(x = year, y = average_rating)) +
  geom_point() +
  labs(title = "Yıllık Ortalama Puanlar")

# Yıllara göre çıkan film sayısını gösteren bir saçılma grafiği oluşturun
ggplot(yearly_averages, aes(x = year, y = movie_count)) +
  geom_point() +
  labs(title = "Her Yıl Yayınlanan Film Sayısı")


```


Over time, it shows an upward trend in ratings.



# d-)
```{r}
#| code-fold: true
#| code-summary: "Show the code"

# Korelasyon hesaplama ve eksik değerleri ele alma
correlation_votes_ratings <- cor(movies$vote, movies$rating, use = "complete.obs")

# Scatter plot oluşturma
library(ggplot2)

ggplot(data = na.omit(movies), aes(x = vote, y = rating)) +
  geom_point() +
  labs(
    title = "Korelasyon: Oy Sayısı vs. IMDb Değerlendirmesi",
    x = "Oy Sayısı",
    y = "IMDb Değerlendirmesi"
  ) +
  theme_minimal()

# Korelasyon değerini yazdırma
cat("Korelasyon Değeri:", correlation_votes_ratings)


# Korelasyon hesaplama ve eksik değerleri ele alma
correlation_votes_ratings <- cor(movies$vote, movies$rating, use = "complete.obs")

# Scatter plot oluşturma
library(ggplot2)

ggplot(data = na.omit(movies), aes(x = vote, y = rating)) +
  geom_point() +
  labs(
    title = "Korelasyon: Oy Sayısı vs. IMDb Değerlendirmesi",
    x = "Oy Sayısı",
    y = "IMDb Değerlendirmesi"
  ) +
  theme_minimal()


```

The correlation coefficient, which is determined as 0.1075729, is quite low. Therefore, we can conclude that there is a weak linear relationship between Ratings and Votes.



# e-)
```{r}
#| code-fold: true
#| code-summary: "Show the code"

# Korelasyon hesaplama
correlation_duration_rating <- cor(movies$duration, movies$rating, use = "complete.obs")

# Korelasyon değerini yazdırma
cat("Korelasyon Değeri:", correlation_duration_rating)

ggplot(data = movies, aes(x = duration, y = rating)) +
  geom_jitter() +
  labs(x = "Duration (Dakika)", y = "Rating") +
  ggtitle("Duration vs. Rating Scatterplot")

```

With a correlation value of 0.008795358, it has a significantly low value. Therefore, we can conclude that there is a weak linear relationship between Durations and Votes at the 1% significance level.



### Question 4

```{r}
#| code-fold: true
#| code-summary: "Show the code"



```
comment   





# • 


```{r}
#| code-fold: true
#| code-summary: "Show the code"



```
comment   



